A Constraint Solving Approach to Parikh Images of Regular Languages

### 2024-03-06 example.tex
Title case

\subsection{Translating the constraints into a Parikh automata intersection problem}

@@

\subsection{Solving the Parikh automata intersection problem using \Calculus{}}

@@

\subsubsection{Approximating paths through automata using flow analysis}\label{sec:a_1}

@@

\subsubsection{Arithmetic flow simplification}\label{sec:intuition:algebra}

@@

\subsubsection{Case Splitting and connectivity propagation}\label{sec:intuition:split}
We now have a choice of two paths through automaton $\mathcal{B}$; the
upper through state $A$ or the lower through state $B$. Since
arithmetic reasoning and propagation are not able to resolve this choice,
we perform a case split by selecting a transition variable that would disconnect
some strongly connected component of automaton $\mathcal{B}$, in this case the transition
from~$I_B$ to state $B$ guarded by variable~$x_{12}$.
 We split the reasoning into the cases $x_{12} > 0$ (transition used)
and $x_{12} = 0$ (transition unused). For presentation, we focus
on the latter case, as the former can be handled in a similar way.

@@

\subsubsection{Computing products}\label{sec:intuition:materialise}
After discounting all transitions that can no longer be taken, we are
left with two (small) flat automata, and can compute their product with
relative ease. By putting off computing the product $\mathcal{B} \times \mathcal{A}'$ until after
performing linear reasoning, and using that to prune transitions, we
have computed a smaller product than we would have with an eager
approach. Computing the product, we will immediately notice that the
$\Char{d}$-labelled transition of automaton $\mathcal{A}'$ has no correspondence
in $\mathcal{B}$, leading to an empty product. We can close the proof goal and
backtrack, and we will eventually derive that the imposed constraints are
unsatisfiable by repeating the same process on the other branch.

>>>>

\subsection{Translating the Constraints into a Parikh Automata Intersection Problem}

@@

\subsection{Solving the Parikh Automata Intersection Problem Using \Calculus{}}

@@

\subsubsection{Approximating Paths Through Automata Using Flow Analysis}\label{sec:a_1}

@@

\subsubsection{Arithmetic Flow Simplification}\label{sec:intuition:algebra}

@@

\subsubsection{Case Splitting and Connectivity Propagation}\label{sec:intuition:split}
We now have a choice of two paths through automaton $\mathcal{B}$; the
upper through state $A$ or the lower through state $B$. Since
arithmetic reasoning and propagation are not able to resolve this choice,
we perform a case split by selecting a transition variable that would disconnect
some strongly connected component of automaton $\mathcal{B}$, in this case the transition
from~$I_B$ to state $B$ guarded by variable~$x_{12}$.
 We split the reasoning into the cases $x_{12} > 0$ (transition used)
and $x_{12} = 0$ (transition unused). For presentation, we focus
on the latter case, as the former can be handled in a similar way.

@@

\subsubsection{Computing Products}\label{sec:intuition:materialise}
After discounting all transitions that can no longer be taken, we are
left with two (small) flat automata, and can compute their product with
relative ease. By putting off computing the product $\mathcal{B} \times \mathcal{A}'$ until after
performing linear reasoning, and using that to prune transitions, we
have computed a smaller product than we would have with an eager
approach. Computing the product, we will immediately notice that the
$\Char{d}$-labelled transition of automaton $\mathcal{A}'$ has no correspondence
in $\mathcal{B}$, leading to an empty product. We can close the proof goal and
backtrack, and we will eventually derive that the imposed constraints are
unsatisfiable by repeating the same process on the other branch.
